Group 9 Presentation

### 2021-12-07 presentation.Rmd
CHANGES

## Data

@@

@@

+ Normal: Normal

@@

## RF

Henrique's RF

@@

ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())
```

@@

```{r, fig.height=5,fig.width=10}
reptree <- ReprTree(rf_fit, train, metric='d2')
plot(reptree, index=1)

@@

## Bagging
```{r}

@@

#Visulizaton of bagging
VI <- data.frame(var=names(test[,-1]), imp=varImp(bagging))

@@

#visualize variable importance with horizontal bar plot
barplot(VI_plot$imp.0,
        names.arg=rownames(VI_plot),
        horiz=TRUE,
        col='steelblue',
        xlab='Variable Importance')

>>>>

## Data {.smaller}

@@

## Data {.smaller}

@@

++ Normal: Normal

@@

## Random Forest

@@

## Random Forest

- Variable importance shows.

```{r}
ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy,fill=variables))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())
```

@@

## Tree
```{r fig.height=7, fig.width=15, message=FALSE, warning=FALSE,echo=FALSE}
reptree <- ReprTree(rf_fit, train, metric='d2')

plot(reptree, index=1)

@@

## Bagging
```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}

@@

#Visulizaton of bagging
VI <- data.frame(var=names(test[,-12]), imp=varImp(bagging))

@@

#visualize variable importance with horizontal bar plot
#barplot(VI_plot$imp.0,
   #     names.arg=rownames(VI_plot),
    #    horiz=TRUE,
     #   col='steelblue',
      #  xlab='Variable Importance')

ggplot(VI_plot)+geom_col(aes(x=(rownames(VI_plot)),y=imp.0,fill=rownames(VI_plot)))+coord_flip()+guides(fill=FALSE)+
  labs(x="Variable Name",y="Importance")
